Cosmic web alignments with the shape, angular momentum and peculiar velocities of dark matter halos

### 2014-05-13 paper/main.tex
updates from Nelson

Perhaps the most striking result so far is that the two webs algorithms gives
different results for the alignment of massive halos. This is not
completely unexpected given that the two algorithms are based on
different physical premises to obtain the directions defining the
eigenvectors. However, we investigate the origin of the different
alignment statistics by studying the inter-web alignment.

@@

There are two possible explanations for the discrepancy. The first is
that in this low mass range the signal for the different
environments (mostly filaments and sheets) is mixed, diluting the
strength of the alignment. Another possible explanation can be
appreciated by carefully looking at the results for different
resolutions.  The $512^3$ grid does show a small anti-alignment for
low  mass haloes indicating that this signal could be related to scales
smaller than $1\hMpc$.  This would be consistent with
\citep{Paz2008} where, using a different technique, they find an
alignment for low mass haloes with the structure on small scales, and
an anti-alighment at large scales (the 2-halo term). The diversity of
results could be then interpreted as a high sensitivity of the
alignment signal to the small scale cosmic web description, including
numerical choices as to how the relevant fields are interpolated.

>>>>

Perhaps the most striking result so far is that the two web algorithms give
different results for the alignment of massive halos. This is not
completely unexpected given that the two algorithms are based on
different physical premises to obtain the directions defining the
eigenvectors. However, we investigate the origin of the different
alignment statistics by studying the inter-web alignment.

@@

There are two possible explanations for the discrepancy. The first is
that in this low mass range the signal for the different
environments (mostly filaments and sheets) is mixed, diluting the
strength of the alignment. Another possible explanation can be
appreciated by carefully looking at the results for different
resolutions.  The $512^3$ grid does show a small anti-alignment for
low  mass haloes indicating that this signal could be related to scales
smaller than $1\hMpc$.  This would be consistent with
\cite{Paz2008} where, using a different technique, they find an
alignment for low mass haloes with the structure on small scales, and
an anti-alighment at large scales (the 2-halo term). The diversity of
results could be then interpreted as a high sensitivity of the
alignment signal to the small scale cosmic web description, including
numerical choices as to how the relevant fields are interpolated.
